### 2020-01-26 README.Rmd
Leaving breadcrumbs
Plugging along add_spatial_info()

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
```

@@

@@

@@

**Joint**:

@@

>>>>

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
# devtools::install_github("rvalavi/blockCV")
library(blockCV)
```

@@

We first load and preprocess the data corresponding to the two census reflecting the time period over which we consider growth in dbh. We load them into R as "tibble" data frames thereby ensuring a standardized input/output format that can be used across all `tidyverse` packages @tidyverse. Furthermore, we ensure that the different variables have the correct names, types (`dbl`, `data`, `factor`).

@@

We then combine the two census data frames into a single data frame  that now includes a numerical variable `growth` reflecting the average annual growth of dbh in cm. Furthermore, variables that (in theory) remain unchanged between censuses appear only once, such as `gx`, `gy`, species-related variables. Variables that should change between censuses are tagged with `1/2` indicating earlier/later, such as `dbh1/dbh2`, `codes1/codes2`.

The resulting data frames are named with some variation of `growth_df`.

@@

**EDA of both BigWoods & SCBI*: Note the large variation in growths for the SCBI trees over the BigWoods trees.

@@

### Add spatial information

We now add spatial information to the `growth_df` data frame. Specifically:

1. In order to control for study region "edge effects" (cite Waller?), we need a function that adds "buffers" of trees. In our case, since our model of interspecies competition relies on a spatial definition of who is a "neighboring competitor" and certain explanatory varibles such as biomass are cummulative, we need to ensure that all trees being modeled are not biased to have different neighbor structure, in particular the trees at the boundary of study regions.
1. Assign each tree to a "fold" for cross-validation purposes. Conventional cross-validation schemes assign observations to folds by resampling individual observations at random. However, underlying this scheme is an assumption that the observations are independent. In the case of forest census data, observations exhibit spatial autocorrelation, and thus this dependence must be incorporated in our resampling scheme @roberts2017 @pohjankukka2017. Packages that have implemented spatial cross-validation include @valavi2019

Thus, before we can incorporate the above information to `growth_df`, we need to define two constants:

```{r}
cv_fold_size <- 100
max_dist <- 7.5
```

For a focal tree of interest, the `max_dist` of `r max_dist` meters acts as a radius defining a neighborhood within which all trees are considered competitors. In other words, all trees within `r max_dist` meters of the focal tree are considered competitor trees. Other studies have estimated this distance; we used `r max_dist` meters as an average of estimated values [@canham2004, @canham2006, @uriarte2004, @tatsumi2013]. Following Tobler's first law of geography that "everything is related to everything else, but near things are more related than distant things." @tobler1970firstlawofgeo, we assume that the degree of spatial autocorrelation is inversely-related to distance. However, we further assume that once trees are more than `r max_dist` meters apart, this autocorrelation is negligeable.

Using the [`blockCV`](https://github.com/rvalavi/blockCV) package, in particular the example code in the package [vignette](http://htmlpreview.github.io/?https://github.com/rvalavi/blockCV/blob/master/vignettes/BlockCV_for_SDM.html), we

* Define the blocking structure
* Determine the degree of spatial autocorrelation for various `max_dist` values

```{r}
# spatial blocking by specified range with random assignment

```

If the above doesn't work, the go back to what we used for PLOS paper.

```{r, cache = TRUE}

```

```{r, cache = TRUE}
```
